Time Series Forest (TSF) and 
its successor, the Supervised Time
Series Forest (STSF), show both 
complementary advances in
classifying time series. 
The goal is the same: 
Achieve interpretable, 
accurate classification in linear 
time complexity. They manage to use 
simple changes to existing algorithms to 
build decision trees without 
resorting to overly complex feature
engineering. TSF introduces the 
core insight of using randomly 
sampled interval values with a 
custom splitting criterion, which 
outperforms previous algorithms 
built on entropy gain. This simple 
adjustment enables TSF to outperform
strong baselines like NN-DTW on a 
wide range of benchmarks, while preserving
the key advantage of interpretability
via temporal importance curves.

The reliance on purely random feature 
generation limits TSF in settings where
the relevant temporal structure is 
sparse or subtle. Precision is sacrificed
for robustness. Also, while being conceptually
elegant, the temporal importance curve
is biased toward central indices due 
to interval frequency effects. TSF 
does not introduce a mechanism for 
normalizing or filtering out these uninformative
peaks.

These issues are addressed in the 
construction of STSF, by replacing
node-level feature randomness with 
tree-level interval supervision. 
A pre-search of the entire time series
using a Fisher score-based strategy
is used to identify candidate discriminatory
intervals. It also further enhances
coverage through multiple time series representation.
These mechanisms increase both precision
and efficiency, resulting in STSF
achieving better accuracy than TSF while
being an order of magnitude faster on
long series.

Despite these improvements, STSF 
comes with new costs: interpretability
suffers and especially the frequency-domain and
derivative-based representations make
semantic mapping harder for practitioners.


In sum, TSF and STSF show that it 
is possible to build time series
classifiers that combine competitiveness with
interpretability. TSF leverages randomness to
ensure robustness and simplicity and
STSF introduces supervision to increase
focus and precision. They establish
a foundation for interval-based
methods that are both practical and
transparent. Their success suggests
that refining how and where information
is extracted within the time series
is preferable to increasing complexity.